A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
correction in back-transformations of effect, se, and CI

intercept <- round(PMsev_mvSQ$b, 4)[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = round(sqrt(abs(PMsev_mvSQ$b)), 4),
   se = round(sqrt(abs(PMsev_mvSQ$se)), 4),
   CI_lower = round(sqrt(abs(PMsev_mvSQ$ci.lb)), 4),
   CI_upper = round(sqrt(abs(PMsev_mvSQ$ci.ub)), 4),
   z_val = round(sqrt(abs(PMsev_mvSQ$zval)), 4),
   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
   eff_bar = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$b)/intercept)),4)*100,
   eff_CI_high = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.ub)/intercept)),4)*100,
   eff_CI_low = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.lb)/intercept)),4)*100

>>>>

intercept <- PMsev_mvSQ$b[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
      "Intercept / No Spray control",
      "Early",
      "Late",
      "Late+",
      "Recommended",
      "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
                   round(
                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
                   )),
   se = round(
      sqrt(
         ifelse(PMsev_mvSQ$b == intercept, intercept,
                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
         sqrt(
            ifelse(PMsev_mvSQ$b == intercept, intercept,
                   PMsev_mvSQ$b + intercept)),
      4),
   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
   z_val = round(PMsev_mvSQ$zval, 4),
   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
   eff_bar = round(sqrt(1 - (
      intercept + PMsev_mvSQ$b
   ) / intercept), 4) * 100,
   eff_CI_high = round(sqrt(
      1 - (intercept + PMsev_mvSQ$ci.ub) / intercept
   ), 4) * 100,
   eff_CI_low = round(sqrt(
      1 - (intercept + PMsev_mvSQ$ci.lb) / intercept
   ), 4) * 100
